Appendix 1.F: Analysing global trends in within-country inequality

### 2023-02-01 PhD_pages/data_appendices/1_F_within_country_trends.qmd
Paper 1: shifting adapted code back into shiny app

>>>>

df_lis = pd.read_csv(open_url(url))

#  ---------------------------------
#  ---------- SECTION 3: Specifications -------------
#  ----------------------------------

# make an empty list to add all the varnames
all_vars = list()

# A string to use to separate the source name from the var name
sep = ": "

# for each df in 'data'
for k,v in data.items():

  # make a list of varnames
  vars = list(v.columns)

  # remove the id cols
  vars.remove(reference_col)
  vars.remove(group_by_col)

  # append the name of the source (the key of 'data') at the front
  vars = [f'{k}{sep}' + var for var in vars]

  # append to the running list
  all_vars = all_vars + vars

app_ui = ui.page_fluid(
    {"class": "p-4"},
    ui.row(
        ui.column(
            4,
            panel_box(
                ui.input_slider("reference_vals", "Reference years", 1975, 2020, value=[1990,2018]),
                ui.input_numeric(
                            "max_dist_from_refs",
                            "=/- (years)",
                            4,
                        ),
                ui.input_numeric(
                            "min_dist_between",
                            "Min distance between observations (years)",
                            23,
                        ),
                ui.input_selectize(
                  "metrics", "Metrics", all_vars, multiple=True
                  ),
                ui.input_checkbox("all_metrics_requirement", "Show only countries with data for all metrics", True),
                ui.input_action_button(
                    "download", "Download data and image", class_="btn-primary w-100"
                ),
            ),
        ),
        ui.column(
            8,
            ui.output_plot("example_plot")
            ),
    ),
)

          source = data_to_match["sources"][i]
          var = data_to_match["var_names"][i]

          df = data[source]

      def prep_plot_and_tables(
        data_to_match,
        reference_vals, 
        max_dist_from_refs,
        min_dist_between,
        reference_col,
        group_by_col,
        tolerance,
        outlier_cut_off_upper,
        all_metrics_requirement):

        # Apply metrics requirement (whether to include only observations with data from all metrics)
        if all_metrics_requirement:
          plot_data = plot_data.loc[plot_data['source_count'] == plot_data['source_count'].max()]

      def prep_selected_vars(selected_vars):

        # selected_vars = [
        #   'LIS: Top_10_share_equiv_market',
        #   'WID: Bottom_50_share_posttax_dis',
        #   'PIP: Top_10_share']

        selected_sources = [var.split(sep, 1)[0] for var in selected_vars]
        selected_var_names = [var.split(sep, 1)[1] for var in selected_vars]

        match_data = {
          "sources": selected_sources,
          "var_names": selected_var_names
          }

        return match_data

      data_to_match = prep_selected_vars(input.metrics())

      plot_and_tables = prep_plot_and_tables(
        data_to_match = data_to_match,
        reference_vals = list(input.reference_vals()), 
        max_dist_from_refs = input.max_dist_from_refs(),
        min_dist_between = input.min_dist_between(),
        reference_col = reference_col,
        group_by_col = group_by_col,
        tolerance = tolerance,
        outlier_cut_off_upper = outlier_cut_off_upper,
        all_metrics_requirement = input.all_metrics_requirement()
        )
